\documentclass[a4paper, 11pt]{article}
\usepackage[utf8]{inputenc}

\newcommand{\ilc}[1]{\texttt{#1}} % inline-code

\title{Proposal: Unidirectional NCM}
\author{Andreas Bauer, Lion Steger}
\date{January 2021}

\begin{document}

    \maketitle

    \section{Objective}\label{sec:objective}
    As of now, the NCM module features bidirectional sessions only.
    Our goal is to replace the current session handling with unidirectional session handling.
    \\

    For this change we need to consider the following components: the underlying random linear network coding library (\ilc{rlnc}),
    session management (\ilc{session.c}) and generation management (\ilc{generation.c}).
    \\

    The \ilc{rlnc} library can presumably be used as is, by simply ignoring the reverse direction of the coding matrix.
    Optionally we might consider taking steps to make use of the full coding matrix.

    Session and generation management on the other hand is to be reengineered from scratch.
    The rewrite will include designing a revised acknowledgment scheme to fit the unidirectional coding scheme.

    \section{Milestones}\label{sec:milestones}
    \begin{enumerate}
        \item Abstract formulation of encoding and acknowledgment scheme, drafting the changes to be made.
        \item First prototype: Incorporates the formulated encoding and acknowledgement scheme.
                Required functionality: Supports transmission of an ICMP Echo Request/Response.
        \item Optional: Reengineer the rlnc instead of ignoring the reverse direction of the coding matrix.
        \item Final version supporting full functionality of the bidirectional version.
        \item Final presentation.
    \end{enumerate}

    \section{Timeline}\label{sec:timeline}
    \begin{itemize}
        \item Beginning of February: Understanding the current code base using bidirectional sessions and refresh understanding of linear coding schemes
        \item Mid February: Milestone 1.
        \item Beginning of March: Implementation of the session and generation logic (Milestone 2.)
        \item March 24th: Milestone: Final version ready (Milestone 4.)
        \item March 31st Final deadline
        \item Beginning of April: Prepare the final presentation (Milestone 5.)
    \end{itemize}

\end{document}
